The human in the loop: volunteer computing as a socio-technical system

### 2016-03-09 PPSN2016/paper.Rnw
Solved data frame issue and plotted some things

\begin{document}
\title{The human in the loop: volunteer computing as a socio-technical
system}

>>>>

\begin{document}

<<setup, cache=FALSE,echo=FALSE>>=
library("ggplot2")
experiment.data <- data.frame(Experiment=character(),
                                 newgraph = character(),
                                 nooverlap = character(),
                                 reboot = character(),
                                 cachereboot = character(),
                                 milliseconds=character(),                           
                                 IPs=character(), 
                                 actualIPs=character(),
                                 PUTs=character(),
                                 actualPUTs=character())

these.experiments <- c("nooverlap-1","nooverlap-newgraph", "nooverlap-newgraph-2","nooverlap-newgraph-3","nooverlap-newgraph-reboot")

for ( i in these.experiments ) {
    print(i)
    this.data <- read.csv(paste0("../data/2016-PPSN/ips-time-cache-2016-03-cache=32-",i,".csv"))
    newgraph = TRUE
    nooverlap = TRUE
    reboot = TRUE
    cachereboot = TRUE

    experiment.data <- rbind( experiment.data,
                             data.frame( Experiment=rep(i, length(this.data$IPs)),
                                        newgraph = rep(newgraph, length(this.data$IPs)),
                                        nooverlap = rep(nooverlap, length(this.data$IPs)),
                                        reboot = rep(reboot, length(this.data$IPs)),
                                        cachereboot = rep(cachereboot, length(this.data$IPs)),
                                        milliseconds=as.integer(this.data$milliseconds),
                                        IPs=as.integer(this.data$IPs),
                                        actualIPs=as.integer(this.data$actualIPs),
                                        PUTs=as.integer(this.data$PUTs),
                                        actualPUTs=as.integer(this.data$actualPUTs)))
}

@
\title{The human in the loop: volunteer computing as a socio-technical
system}
